A few stickleback suffice to transport adaptive alleles to new lakes

### 2018-12-10 Stickleback_Paper.tex

\begin{center}
\begin{tabular}{ | c | c  | c  | c | }
 \hline
 $m = 0.01$ & $m = 0.1$ & $m = 1.0$ & $m = 10.0$ \\ 
 $-0.1227$ &  $-4.6976$ & $-12.9298$  & $-12.2710$\\
 \hline
\end{tabular}
\end{center}

>>>>

\begin{table}[ht]
    \centering
    \begin{tabular}{rrrrr}
      \hline
     & m=0.01 & m=0.1 & m=1 & m=10 \\ 
      \hline
          best & 2.77 & -12.02 & -21.02 & -7.02 \\ 
      expected & 4.22 & -4.78 & -14.64 & -5.47 \\ 
       \hline
    \end{tabular}
    \caption{
        Haplotypic variation present in the new lakes at time of colonization,
        across rates of gene flow.
        \textbf{``Best''} shows the most negative trait value achievable
            with intact haplotypes, averaged across populations.
        \textbf{``Expected''} shows the trait value
            achieved by averaging haplotypic values weighted by fitness
            (see text for details).
        This suggests that populations at $m=1$ have sufficient genetic variation
        to completely adapt (reach $-10$) using intact haplotypes,
        while at $m=0.1$ variation must be released from haplotypes by recombination.
    } \label{tab:linkage}
\end{table}
